Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-26 pirouette_article.tex
Add feedback @rsetienne in text

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confusion when the generative model is the
	generative model. Giovanni, what do you think?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}

>>>>

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confusion when the generative model is the
	generative model. Giovanni, what do you think?
}
\rampal{
	This explanation again does not resolve the confusion. 
	You have a new model with which you generate a tree and the alignment. 
	In the pirouette paper this is DD. You could call this the generative model. 
	You also create a twin tree using a standard tree prior, e.g. BD. 
	Then in inference you use a tree prior, e.g. Yule. I think what you mean 
	is that Yule is not the one used for the twin tree, 
	and is therefore not the generative tree model. 
	But this is far from clear as it could also refer to the DD model. 
	Perhaps if you replace by "generative model for the twin tree", 
	then it is fine. Note that comparison model or baseline model 
	are NOT synonyms.
}
\rampal{
	Not synonyms for the generative tree model for the twin tree, I mean.
}
\richel{
	Giovanni, could you process this feedback?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}
